---
title: "Final project code"
author: "Team AI"
date: '2022-06-24'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### import
```{r,message=FALSE}
library(tidyverse)
library(caTools)
library(randomForest)
library(caret)
library(e1071)
library(rpart)
library(tidymodels)
library(schrute)
library(lubridate)
library(quantreg)
library(pROC)
library(klaR)
library(psych)
library(MASS)
library(devtools)
library(ROCR)
```
### Data:
```{r}
dataset = read.csv("C:\\Tal\\Data Engineer\\BSc\\semester 4\\Advanced programming\\project\\children_at_risk\\data\\Children_at_risk.csv")
datasetA <- dataset %>%
  filter(Test == 'A') %>% 
  mutate(Hope_A = Q1+Q2+Q3+Q4+Q5+Q6+Q7+(5-Q8)+Q9+(5-Q10)+(5-Q11)) %>% 
  dplyr::select(Id,Hope_A)

datasetB <- dataset %>%
  filter(Test == 'B') %>% 
  mutate(Hope_B = Q1+Q2+Q3+Q4+Q5+Q6+Q7+(5-Q8)+Q9+(5-Q10)+(5-Q11)) %>% 
  dplyr::select(Id,Hope_B)

datasetC <- dataset %>%
  filter(Test == 'C') %>% 
  mutate(Hope_C = Q1+Q2+Q3+Q4+Q5+Q6+Q7+(5-Q8)+Q9+(5-Q10)+(5-Q11)) %>% 
  dplyr::select(Id,Hope_C)

dataset = left_join(dataset,left_join(datasetA,left_join(datasetB,datasetC)))
dataset <- dataset %>%
  mutate(n_of_t = T1+T2+T3+T4+T5+T6+T7+T8+T9+T10,Hope = Q1+Q2+Q3+Q4+Q5+Q6+Q7+(5-Q8)+Q9+(5-Q10)+(5-Q11))
```


### Inital hypothesis tests:

- test 1:
Compare the Hope at first survey and third 
```{r}
Hope_1 <- dataset %>%
  filter(Test == 'A') %>% 
  dplyr::select(Hope)

Hope_3 <- dataset %>%
  filter(Test == 'C') %>% 
  dplyr::select(Hope)

t.test(Hope_3$Hope,Hope_1$Hope,paired = TRUE ,alternative = 'greater')
```
- test 2:
Compare the change of Hope from second to first survey among children who served and doesn't served
```{r}
army_1 <- dataset %>%
  filter(Test == 'A' ,(A4 == 1 | A5 == 1)) %>% 
  dplyr::select(Hope)

army_3 <- dataset %>%
  filter(Test == 'B' ,(A4 == 1 | A5 == 1)) %>% 
  dplyr::select(Hope)

no_army_1 <- dataset %>%
  filter(Test == 'A', A4 == 0,A5 == 0) %>% 
  dplyr::select(Hope)

no_army_3 <- dataset %>%
  filter(Test == 'B', A4 == 0,A5 == 0) %>% 
  dplyr::select(Hope)

vec1 = army_3$Hope - army_1$Hope
vec2 = no_army_3$Hope - no_army_1$Hope


t.test(vec1,vec2,paired = FALSE ,alternative = 'greater')
```

### Regression models:

Predicting the Hope at third survey
```{r}
# Selecting the features
reg_data = dataset %>% 
  filter(Test == 'A') %>% 
  dplyr::select(Religiousness,Permanency,A4,n_of_t,Hope_A,Hope_B,Hope_C)

# Setting seed
set.seed(1234)

# Splitting the data train-test split
split = sample.split(reg_data$Hope_C, SplitRatio = 0.8)
training_set = subset(reg_data, split == TRUE)
test_set = subset(reg_data, split == FALSE)
```

- Model 1 Random forest:
```{r}
# Create regressor
RF_regressor = randomForest(x = training_set[-7],
                         y = training_set$Hope_C,
                         ntree = 100)
# Predict test result
y_pred = predict(RF_regressor, test_set[-7])

# Calculate MSE
e = test_set[7] - y_pred
e2 = e*e
mse = mean(e2$Hope_C)

# Calculate RSQR
res <- caret::postResample(test_set[7],y_pred)
rsq <- res[2]

# Print results
print(paste0("Random forest- MSE: ",mse))
print(paste0("Random forest- RSQR: ",rsq))
```
- Model 2 SVR:
```{r}
# Create regressor
SVR_regressor = svm(formula = Hope_C ~ .,
                data = training_set,
                type = 'eps-regression',
                kernel = 'radial')

# Predict test result
y_pred = predict(SVR_regressor, test_set[-7])

# Calculate MSE
e = test_set[7] - y_pred
e2 = e*e
mse = mean(e2$Hope_C)

# Calculate RSQR
res <- caret::postResample(test_set[7],y_pred)
rsq <- res[2]

# Print results
print(paste0("SVR- MSE: ",mse))
print(paste0("SVR- RSQR: ",rsq))
```
- Model 3 Decision tree:
```{r}
# Create regressor
DT_regressor = rpart(formula = Hope_C ~ .,
                  data = training_set,
                  control = rpart.control(minsplit = 15))

# Predict test result
y_pred = predict(DT_regressor, test_set[-7])

# Calculate MSE
e = test_set[7] - y_pred
e2 = e*e
mse = mean(e2$Hope_C)

# Calculate RSQR
res <- caret::postResample(test_set[7],y_pred)
rsq <- res[2]

# Print results
print(paste0("Decision tree- MSE: ",mse))
print(paste0("Decision tree- RSQR: ",rsq))
```
- Model 4 Linear Regression:
```{r}
# Create regressor
LM_regressor = lm(formula = Hope_C ~ .,
               data = training_set)

# Predict test result
y_pred = predict(LM_regressor, test_set[-7])

# Calculate MSE
e = test_set[7] - y_pred
e2 = e*e
mse = mean(e2$Hope_C)

# Calculate RSQR
res <- caret::postResample(test_set[7],y_pred)
rsq <- res[2]

# Print results
print(paste0("Random forest- MSE: ",mse))
print(paste0("Random forest- RSQR: ",rsq))
```
- Model 5 Quantile regression:
```{r}
# Create regressor
Quan_regressor <- rq(Hope_C ~ ., data = training_set)

# Predict test result
y_pred = predict(Quan_regressor, test_set[-7])

# Calculate MSE
e = test_set[7] - y_pred
e2 = e*e
mse = mean(e2$Hope_C)

# Calculate RSQR
res <- caret::postResample(test_set[7],y_pred)
rsq <- res[2]

# Print results
print(paste0("Quantile regression- MSE: ",mse))
print(paste0("Quantile regression- RSQR: ",rsq))
```
### Additinal hypothesis test
```{r}
H_data = dataset %>% 
  filter(Test == 'A') %>% 
  mutate(served = ifelse(A4==1|A5==1,1,0)) %>% 
  mutate(Hope_A = ifelse(Hope_A>median(dataset$Hope_B),1,0),Hope_B = ifelse(Hope_B>median(dataset$Hope_B),1,0)) %>% 
  dplyr::select(Religiousness,Permanency,n_of_t,served,Hope_A,Hope_B)

Hope_1 <- H_data %>%
  filter(served == 1) %>% 
  dplyr::select(Hope_B)

Hope_3 <- H_data %>%
  filter(served == 0) %>% 
  dplyr::select(Hope_B)

t.test(Hope_1$Hope_B,Hope_3$Hope_B,paired = FALSE ,alternative = 'greater')
```



### Classification models:

Predicting whether the hope of the child will increase or decrease in the second survey

```{r}

# Selecting the features
CL_data = dataset %>% 
  filter(Test == 'A') %>% 
  mutate(served = ifelse(A4==1|A5==1,1,0)) %>% 
  mutate(Hope_A = ifelse(Hope_A>median(dataset$Hope_B),1,0),Hope_B = ifelse(Hope_B>median(dataset$Hope_B),1,0)) %>% 
  dplyr::select(Religiousness,Permanency,n_of_t,served,Hope_A,Hope_B)

# Factor the binary feature
CL_data$Hope_B = as.factor(CL_data$Hope_B)

# Setting seed
set.seed(123)

# Splitting the data train-test split
training.samples <- CL_data$served %>% 
  createDataPartition(p = 0.7, list = FALSE)
train.data  <- CL_data[training.samples, ]
test.data <- CL_data[-training.samples,]

# Create classifier
# Set CV with 5 folds
trainC = trainControl(method = "cv",number = 5,savePredictions = T )
model <- train(Hope_B ~. , data = train.data,method="glm", family = "binomial",trControl = trainC)
summary(model)
model
probabilities <- model %>% predict(test.data, type = "prob")
```

```{r}

# Predict test result
pred = prediction(probabilities$'1', test.data$Hope_B)

# Create ROC curve
roc = performance(pred,"tpr","fpr")
plot(roc, colorize = T, lwd = 2)
abline(a = 0, b = 1) 

# Create PR curve
pr = performance(pred,"prec","rec")
plot(pr, colorize = T, lwd = 2)
abline(a = 0.5, b=0) 

# Find the best threshold
prediction(probabilities[2], test.data$Hope_B) %>%
  performance(measure = "tpr", x.measure = "fpr") -> result

plotdata <- data.frame(x = result@x.values[[1]],
                       y = result@y.values[[1]], 
                       p = result@alpha.values[[1]])

dist_vec <- plotdata$x^2 + (1 - plotdata$y)^2
opt_pos <- which.min(dist_vec)

print(paste0("Best threshold is: p = ",round(plotdata[opt_pos, ]$p, 3)))

```
```{r}
# Create confusion matrix
cm = table(test.data$Hope_B, probabilities$`1` > 0.343)
cm
```
